Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-07-05 ProbabilisticCoherence.tex
Minor cleanup of coherence section

It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints.  We follow other authors \cite{Wickramasuriya2017}\todo{FPP?} in using the nomenclature {\em coherence} to describe this property.   
%While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.

We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem thus facilitating the development of the probabilistic forecast reconciliation in section~\ref{sec:reconciliation}.

Recall that $\bm{y}_t \in \mathbb{R}^n$ is a $n$-dimensional time series subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.

@@

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  The measure $\breve{\nu}$ is coherent if it has the property
  $$
      \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall  \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
    $$    
\end{definition}
A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{y_{t+h|h}}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.

>>>>

It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints.  We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature {\em coherence} to describe this property.   
%While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem thus facilitating the development of the probabilistic forecast reconciliation in section~\ref{sec:reconciliation}.

@@

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
  The measure $\breve{\nu}$ is coherent if it has the property
  $$
      \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall  \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
    $$    
\end{definition}
A probabilistic forecast for time $t+h$ is coherent if uncertainty in ${\bm y}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
